Usenet Project - CSV Cleaning

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
cleaned up csv cleaning code

## Loading Libraries
```{r}
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
# Load necessary library
library(dplyr)
# Load necessary libraries
library(ggplot2)
library(dplyr)
```
## Read and Clean CSVs
```{r}
# Load Directories
output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"

# Load the datasets
all_threads <- read.csv(file.path(threads_directory, "combined_threads.csv"))
all_comments <- read.csv(file.path(comments_directory, "combined_comments.csv"))

# Assign unique identifiers to newsgroups
newsgroup_ids <- c("netmed" = "NG01", "netmotss" = "NG02", "netnews" = "NG03",
                   "netpolitics" = "NG04", "netreligion" = "NG05", "netsingles" = "NG06")

@@

# Display the updated dataframes (optional)
head(all_threads)
head(all_comments)
```
## Fix Date and Time Columns
```{r}
# Function to clean the datetime strings
clean_datetime <- function(dt_str) {
  gsub("[^[:alnum:] [:punct:]]", "", dt_str)
}

@@

all_threads$Date <- as.Date(all_threads$Date, format = "%m/%d/%y")
```

## Run and Sentiment Scores
```{r} 
library(syuzhet)
all_comments <- all_comments %>% mutate(SentimentScore = get_sentiment(Full.Text, method = "afinn"))
```

## Save Cleaned CSVs to File
```{r}
write.csv(all_threads, file.path(threads_directory, "combined_threads_cleaned.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "combined_comments_cleaned.csv"), row.names = FALSE)
```

# Filter Additionally by Keyword
```{r Filter by Keyword}

# List of extended keywords and phrases
keywords <- c("aids", "hiv", "acquired immune deficiency syndrome", "human immunodeficiency virus",
              "gay plague", "gay cancer", "kaposi's sarcoma", "pneumocystis pneumonia",
              "homosexual disease", "gay disease", "gay fear", "fear of gay", "fear of homosexual",
              "sexual orientation disease")

@@

# Table and Figures
```{r Descriptive Statistics}
# Load necessary library
library(dplyr)
library(sjPlot)

# Calculate statistics using dplyr
summary_df <- all_comments %>%
  group_by(newsgroup) %>%
  summarize(
    Threads = n_distinct(Thread.ID),
    Comments = n(),
    Authors = n_distinct(Author),
    Avg_Comments_Per_Thread = Comments / Threads,
    Avg_Sentiment_Score = mean(SentimentScore, na.rm = TRUE)
  )

>>>>

## Maintenance
```{r Load LIbraries, Directories, and Datasets}
# Load Libraries
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
library(ggplot2)
library(dplyr)
library(syuzhet)
library(sjPlot)

# Load Directories
output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"

# Load the datasets
all_threads <- read.csv(file.path(threads_directory, "combined_threads.csv"))
all_comments <- read.csv(file.path(comments_directory, "combined_comments.csv"))
```

```{r Dataset Cleaning}
# Assign unique identifiers to newsgroups
newsgroup_ids <- c("netmed" = "NG01", "netmotss" = "NG02", "netnews" = "NG03",
                   "netpolitics" = "NG04", "netreligion" = "NG05", "netsingles" = "NG06")

@@

# Function to clean the datetime strings
clean_datetime <- function(dt_str) {
  gsub("[^[:alnum:] [:punct:]]", "", dt_str)
}

@@

all_threads$Date <- as.Date(all_threads$Date, format = "%m/%d/%y")

# Display the updated dataframes (optional)
head(all_threads)
head(all_comments)
```

```{r Run and Add Sentiment Scores} 
all_comments <- all_comments %>% mutate(SentimentScore = get_sentiment(Full.Text, method = "afinn"))
```

```{r Save Cleaned CSVs to File}
write.csv(all_threads, file.path(threads_directory, "combined_threads_cleaned.csv"), row.names = FALSE)
write.csv(all_comments, file.path(comments_directory, "combined_comments_cleaned.csv"), row.names = FALSE)
```

# Additional Filtering
```{r Filter by Keyword}
# List of extended keywords and phrases
keywords <- c("aids", "hiv", "acquired immune deficiency syndrome", "human immunodeficiency virus",
              "gay plague", "gay cancer", "kaposi's sarcoma", "pneumocystis pneumonia",
              "homosexual disease", "gay disease", "gay fear", "fear of gay", "fear of homosexual",
              "sexual orientation disease")

@@

# Table and Figures
```{r Descriptive Statistics}
# Calculate statistics using dplyr
summary_df <- all_comments %>%
  group_by(newsgroup) %>%
  summarize(
    Threads = n_distinct(Thread.ID),
    Comments = n(),
    Authors = n_distinct(Author),
    Avg_Comments_Per_Thread = Comments / Threads,
    Avg_Sentiment_Score = mean(SentimentScore, na.rm = TRUE)
  )
